---
title: "Sensitivity analysis-movie reviews (binary) [rerun]"
author: "Yiyu Wang"
date: "2025-09-23"
output:
  html_document:
    df_print: paged
  word_document: defaultss
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
subparagraph: true
urlcolor: blue
linkcolor: black
header-includes:
- \usepackage{graphicx}
- \usepackage{float}
- \usepackage{booktabs}
---

```{r setup, eval = T, echo = F, message=F, warning=F, results='hide'}
library(knitr)
library(kableExtra)
options(width=60)
opts_chunk$set(echo = TRUE, comment="", error=FALSE, 
               #cache.lazy = FALSE, 
               fig.align="center", message=FALSE, warning=FALSE, tidy = FALSE)
```

# 1.2 LLM Sensitivity analysis - movie reviews
### rerun - batch_size = 20

```{r codeblock}
### Setup
library(tidyverse)
library(readr)
library(scales)
library(glue)
```

```{r, eval=FALSE}
# load data (original & rerun: batch_size=20)
# Replace b=20 in fullgrid with rerun1, then
# make before-vs-after comparison plots
full   <- read_csv("llm_results/binary_movie_reviews/movie_tuning_summary_by_params.csv",  show_col_types = FALSE)
rerun1 <- read_csv("llm_results/binary_movie_review_rerun/movie_tuning_batch20_rerun_summary2.csv", show_col_types = FALSE)

# Ensure same columns (order may differ but names must match)
stopifnot(setequal(names(full), names(rerun1)))
# Keep consistent column order as in full
rerun1 <- rerun1[, names(full)]

# replace fullgrid (b=20)
# Keep everything in full except b=20; then append rerun1's b=20 rows
full_b20_fixed <- full %>%
  filter(batch_size != 20 | is.na(batch_size)) %>%          # drop original b=20 rows
  bind_rows(rerun1 %>% filter(batch_size == 20 | is.na(batch_size))) %>%  # add rerun1 b=20
  arrange(dataset, batch_size, temperature, top_p, top_k, max_tokens)

# Save a copy for provenance / downstream plotting scripts
write_csv(full_b20_fixed, "llm_results/binary_movie_review_rerun/movie_tuning_summary_by_params_b20replaced.csv")
```

# Visualization
### 1) Accuracy across batch size & temperature

```{r p1}
# load data
rerun_b20 <- read_csv("llm_results/binary_movie_review_rerun/movie_tuning_summary_by_params_b20replaced.csv")
# Convert some parameters to factors for plotting
rerun_b20  <- rerun_b20  %>%
  mutate(temperature = factor(temperature),
         top_p = factor(top_p),
         top_k = factor(top_k),
         max_tokens = factor(max_tokens),
         batch_size = factor(batch_size))

my_colors <- c("0.1" = "#4C72B0",   
               "0.2" = "#DD8452",   
               "0.5" = "#55A868") 

# p1 - Accuracy vs Batch Size
p1 <- rerun_b20  %>%
  ggplot(aes(x = batch_size, y = accuracy, fill = temperature)) +
  geom_col(position = position_dodge(width = 0.8), na.rm = FALSE) +
  labs(title = "Accuracy across batch size & temperature (Movie dataset)",
       x = "Batch size",
       y = "Accuracy",
       fill = "Temperature") +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_manual(values = my_colors, na.value = "grey70") +
  theme_bw()
p1
```

### 2) Macro F1 across batch size & top_p

```{r p2}
# p2 - Macro F1 vs Batch Size & top_p
top_p_labels <- c("0.8" = "top_p = 0.8",
                  "0.9" = "top_p = 0.9",
                  "1"   = "top_p = 1.0")

p2 <- rerun_b20  %>%
  ggplot(aes(x = batch_size, y = macro_f1, color = temperature, group = temperature)) +
  geom_smooth(method = "loess", se = TRUE, alpha = 0.2, linewidth = 1, na.rm = FALSE) +
  geom_point(size = 2, na.rm = FALSE) +
  facet_wrap(~ top_p, nrow = 1, labeller = labeller(top_p = top_p_labels)) +
  labs(title = "Macro F1 Score by Batch Size & top_p (Movie dataset)",
       x = "Batch size",
       y = "Macro F1 score",
       color = "Temperature", 
       fill = "Temperature") +
  scale_color_manual(values = my_colors, na.value = "grey70") +
  scale_fill_manual(values = my_colors, na.value = "grey70") +
  theme_bw(base_size = 12)
p2
```

### 3) Accuracy Heatmap across parameter combinations (faceted by batch size)

```{r p3a-plot, fig.width=12, fig.height=8}
# p3 - Heatmap of Accuracy
temp_labels <- c("0.1" = "temp. = 0.1",
                 "0.2" = "temp. = 0.2",
                 "0.5" = "temp. = 0.5")

# A: batch size as facet
p3_a <- rerun_b20  %>%
  ggplot(aes(x = max_tokens, y = top_k, fill = accuracy)) +
  geom_tile(color = "white", na.rm = FALSE) +
  labs(title = "Heatmap of Accuracy (top_k * max_tokens) by batch_size (Movie)",
       x = "max_tokens", y = "top_k", fill = "Accuracy") +
  scale_fill_gradient(low = "#f0f9e8", high = "#0868ac", na.value = "grey70",
                      labels = number_format(accuracy = 0.001)) +
  facet_grid(batch_size ~ top_p + temperature,
             labeller = labeller(temperature = temp_labels,
                                 top_p = top_p_labels,
                                 batch_size = label_both)) +
  guides(fill = guide_colorbar(title.position = "top", barwidth = 2)) +
  theme_minimal(base_size = 10) +
  theme(strip.background = element_rect(fill = "#f3f3f3", color = NA),
        strip.text = element_text(face = "bold", size = 8),
        axis.title.x = element_text(size = 14, face = "bold"),
        axis.title.y = element_text(size = 14, face = "bold"))
p3_a
```

### 4) Accuracy Heatmap across parameter combinations (faceted by max_tokens)

```{r p3b-plot, fig.width=12, fig.height=8}
# p3-B: max_tokens as facet; x = batch_size
p3_b <- rerun_b20  %>%
  ggplot(aes(x = batch_size, y = top_k, fill = accuracy)) +
  geom_tile(color = "white", na.rm = FALSE) +
  labs(title = "Heatmap of Accuracy (batch_size * top_k), faceted by max_tokens (Movie)",
       x = "Batch size", y = "top_k", fill = "Accuracy") +
  scale_fill_gradient(low = "#f0f9e8", high = "#0868ac", na.value = "grey70",
                      labels = number_format(accuracy = 0.001)) +
  facet_grid(top_p ~ temperature + max_tokens,
             labeller = labeller(temperature = temp_labels,
                                 top_p = top_p_labels,
                                 max_tokens = label_both)) +
  guides(fill = guide_colorbar(title.position = "top", barwidth = 2)) +
  theme_minimal(base_size = 10) +
  theme(strip.background = element_rect(fill = "#f3f3f3", color = NA),
        strip.text = element_text(face = "bold", size = 8),
        axis.title.x = element_text(size = 14, face = "bold"),
        axis.title.y = element_text(size = 14, face = "bold"))
p3_b
```

### 5) Precision vs Recall

```{r p4}
# p4 - Precision vs Recall
# Threshold for outliers (customizable)
prec_thr <- 0.85
recall_thr <- 0.88

# Identify outliers: any point with low precision OR low recall
outliers <- rerun_b20  %>%
  filter(precision < prec_thr | recall < recall_thr) %>%
  mutate(combo_id = paste0("temp=", temperature,
                           "_top_p=", top_p,
                           "_top_k=", top_k,
                           "_max_tokens=", max_tokens,
                           "_batch=", batch_size))

# PR scatter plot
p_pr <- rerun_b20  %>%
  ggplot(aes(x = precision, y = recall,
             color = temperature, shape = batch_size)) +
  geom_point(size = 3, alpha = 0.8) +
  # Add threshold reference lines
  geom_vline(xintercept = prec_thr, linetype = "dashed", color = "red", size = 0.7) +
  geom_hline(yintercept = recall_thr, linetype = "dashed", color = "red", size = 0.7) +
  # Highlight outliers with labels
  geom_point(data = outliers, aes(x = precision, y = recall), 
             color = "black", fill = "yellow", size = 4, shape = 21, stroke = 1.2) +
  ggrepel::geom_text_repel(data = outliers, aes(x = precision, y = recall, label = combo_id),
                           size = 3, color = "black", max.overlaps = 10) +
  labs(title = "Precision vs Recall across parameter settings (Movie dataset)",
       x = "Precision", y = "Recall",
       color = "Temperature", shape = "Batch Size") +
  theme_bw(base_size = 12)

print(p_pr)
```

### 6) Balanced Accuracy vs MCC

```{r p5}
# p5 - Balanced Accuracy vs MCC 
p5_ba_mcc <- rerun_b20  %>%
  ggplot(aes(x = balanced_accuracy, y = mcc,
             color = top_p)) +
  geom_point(size = 3, alpha = 0.8, na.rm = FALSE) +
  labs(title = "Balanced Accuracy vs MCC (Movie dataset)",
       x = "Balanced Accuracy", y = "MCC",
       color = "top_p") +
  theme_bw(base_size = 12)

print(p5_ba_mcc)
```

### 7) Barchart: Average missing rate vs batch size

```{r p6}
# p6: bar chart - average missing Rate vs Batch Size
p6_miss <- rerun_b20  %>%
  group_by(batch_size) %>%
  summarise(avg_missing = mean(missing_rate, na.rm = TRUE)) %>%
  ggplot(aes(x = batch_size, y = avg_missing, fill = batch_size)) +
  geom_col(na.rm = FALSE) +
  labs(title = "Average Missing Rate by Batch Size (Movie dataset)",
       x = "Batch size", y = "Avg. Missing Rate") +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_brewer(palette = "Set2", na.value = "grey70") +
  theme_bw(base_size = 12)
print(p6_miss)
```

### 8) Failure rate heatmap

```{r p7, fig.width=12, fig.height=8}
# Failure Rate (Missing Rate) Visualization
# Heatmap: missing rate across all parameter combinations, facet by batch_size
p_fail_full_heat <- rerun_b20  %>%
  ggplot(aes(x = max_tokens, y = top_k, fill = missing_rate)) +
  geom_tile(color = "white") +
  labs(title = "Failure Rate Heatmap across parameter combinations (Movie)",
       x = "max_tokens", y = "top_k", fill = "Missing Rate") +
  scale_fill_gradient(low = "#f0f9e8", high = "#d73027",
                      na.value = "grey70",
                      labels = percent_format(accuracy = 1)) +
  facet_grid(batch_size ~ temperature + top_p,
             labeller = labeller(
               temperature = label_both,
               top_p = label_both,
               batch_size = label_both)) +
  theme_minimal(base_size = 10) +
  theme(strip.background = element_rect(fill = "#f3f3f3", color = NA),
        strip.text = element_text(face = "bold", size = 8),
        axis.text.x = element_text(angle = 45, hjust = 1))
print(p_fail_full_heat)
```

### 9) Tables: Top 5 & Bottom 5 parameter combinations

```{r table, echo=FALSE}
# Tables
# Select key columns for reporting
report_cols <- c("temperature", "top_p", "top_k", "max_tokens", "batch_size",
                 "accuracy", "macro_f1", "mcc", "precision", "recall", "missing_rate")

# Rank by macro_f1 (primary), then accuracy, then mcc
ranked_df <- rerun_b20  %>%
  arrange(desc(macro_f1), desc(accuracy), desc(mcc))

# Top-5 best parameter combos
top5 <- ranked_df %>%
  slice_head(n = 5) %>%
  select(all_of(report_cols))

# Bottom-5 worst parameter combos
bottom5 <- ranked_df %>%
  slice_tail(n = 5) %>%
  select(all_of(report_cols))

# Print as tables
cat("===== Top-5 Best Parameter Combos (Movie dataset) =====\n")
print(top5)

cat("\n===== Bottom-5 Worst Parameter Combos (Movie dataset) =====\n")
print(bottom5)
```

### 10) Plot: Top 5 vs Bottom 5 parameter combinations

```{r p8}
# plot: top5 vs bottom5 parameter combos
# Rank by macro_f1 > accuracy > mcc
ranked_df <- rerun_b20  %>%
  arrange(desc(macro_f1), desc(accuracy), desc(mcc)) %>%
  mutate(combo_id = paste0("Combo_", row_number()))  # shorten labels
# Select Top-5 and Bottom-5
top5 <- ranked_df %>% slice_head(n = 5) %>% mutate(group = "Top-5")
bottom5 <- ranked_df %>% slice_tail(n = 5) %>% mutate(group = "Bottom-5")

combo_df <- bind_rows(top5, bottom5) %>%
  select(combo_id, group, macro_f1, missing_rate) %>%
  pivot_longer(cols = c(macro_f1, missing_rate),
               names_to = "metric", values_to = "value")
# Plot dotplot
p_dot <- combo_df %>%
  ggplot(aes(x = value, y = reorder(combo_id, value), color = group)) +
  geom_point(size = 3) +
  facet_wrap(~ metric, scales = "free_x") +
  labs(title = "Top-5 vs Bottom-5 Parameter Combos (Movie)",
       x = "Value", y = "Parameter Combo", color = "Group") +
  theme_bw(base_size = 12)

print(p_dot)
```

